Web Page Visualization Code

### 2024-09-02 Scripts - Data Cleaning and Visuals/New Webpage Visualizations.Rmd
added interactives

```{r R Load Libraries, Directories, and Datasets}
library(tidyverse)
library(ggplot2)
library(dplyr)
library(igraph)
library(ggraph)
library(tidytext)
library(topicmodels)
library(visNetwork)
library(RColorBrewer) 
library(sjPlot)
library(ldatuning)
library(tm)
library(SnowballC)

@@

# Plot the histogram with density overlay using all_threads
ggplot(filtered_threads, aes(x = Thread_Relevancy)) +
  geom_histogram(aes(y = ..count..), binwidth = bin_width, fill = "skyblue", color = "black", alpha = 0.7) + 
  geom_density(aes(y = ..density.. * bin_width * nrow(all_threads)), fill = "orange", alpha = 0.4) +  # Scale density to match histogram counts
  labs(title = "Histogram and Density of Thread Relevancy Scores",
       x = "Relevancy",
       y = "Number of Threads") +
  theme_bw()
```
```{r Get Filtered Comments from Filtered Threads}
# Filter threads with only one comment out of filtered threads 
filtered_threads <- filtered_threads %>%
  filter(Number.of.Messages > 1)

@@

>>>>

```{r R Load Libraries, Directories, and Datasets}
library(tidyverse)
library(ggplot2)
library(dplyr)
library(igraph)
library(ggraph)
library(tidytext)
library(topicmodels)
library(visNetwork)
library(RColorBrewer) 
library(sjPlot)
library(ldatuning)
library(tm)
library(SnowballC)
library(reticulate)

@@

# Plot the histogram with density overlay using all_threads
ggplot(filtered_threads, aes(x = Thread_Relevancy)) +
  geom_histogram(aes(y = ..count..), binwidth = bin_width, fill = "skyblue", color = "black", alpha = 0.7) + 
  geom_density(aes(y = ..density.. * bin_width * nrow(all_threads)), fill = "orange", alpha = 0.4) +  # Scale density to match histogram counts
  labs(title = "Histogram and Density of Thread Relevancy Scores",
       x = "Relevancy",
       y = "Number of Threads") +
  theme_bw()
```

```{r Get Filtered Comments from Filtered Threads}
# Filter threads with only one comment out of filtered threads 
filtered_threads <- filtered_threads %>%
  filter(Number.of.Messages > 1)

@@

```{r Interactive Co-occurrence Network with Plotly, eval=TRUE, include=TRUE}
# Load necessary library
library("threejs")

# Prepare data for 3D network
# We will use the filtered_co_occurrence and term_topic_df from the previous code block

# Create an igraph object from the filtered co-occurrence matrix
graph_3d <- graph_from_adjacency_matrix(filtered_co_occurrence, weighted = TRUE, mode = "undirected", diag = FALSE)

# Simplify the graph to avoid self-loops and redundant edges
graph_3d <- simplify(graph_3d)

# Prepare colors based on topic assignment
topic_colors <- RColorBrewer::brewer.pal(6, "Set1")[term_topic_df$topic]

# Create the 3D force-directed network
network_3d <- graphjs(
  graph_3d,
  vertex.size = log1p(term_frequency[filtered_terms]),
  vertex.label = V(graph_3d)$name,
  vertex.color = topic_colors,
  edge.width = E(graph_3d)$weight / max(E(graph_3d)$weight) * 5,  # Scale edge width
  main = "Interactive 3D Co-occurrence Network of Key Themes in AIDS Discussion"
)

# Save the interactive 3D network to an HTML file
htmlwidgets::saveWidget(network_3d, file = file.path(output_directory, "images and tables/new web visualizations", "interactive_plot_3d_cooccurrence_network.html"))
```

### 2024-09-02 Scripts - Data Cleaning and Visuals/Old Webpage Visualizations.Rmd
added interactives

# Initial Visualizations - Python
```{python Distribution of Comments per Newsgroup}
plt.figure(figsize=(10, 6))
sns.countplot(data=all_comments, x='newsgroup', order=all_comments['newsgroup'].value_counts().index)
plt.title('Distribution of Comments per Newsgroup')
plt.xticks(rotation=45)
plt.tight_layout()
plt.savefig(os.path.join(output_directory, "images and tables/distribution_of_comments_per_newsgroup.png"))
plt.show()
```

@@

plt.figure(figsize=(10, 6))
all_threads.groupby(all_threads['Date'].dt.to_period('M')).size().plot(kind='line')
plt.title('Number of Threads Across All Newsgroups Over Time')
plt.xlabel('Month')
plt.ylabel('Number of Threads')
plt.tight_layout()
plt.savefig(os.path.join(output_directory, "images and tables/number_of_threads_over_time.png"))
plt.show()
```

@@

plt.figure(figsize=(10, 6))
sns.barplot(data=avg_comments_per_thread, x='newsgroup', y='Number.of.Messages', order=avg_comments_per_thread.sort_values('Number.of.Messages', ascending=False)['newsgroup'])
plt.title('Average Number of Comments per Thread by Newsgroup')
plt.xlabel('Newsgroup')
plt.ylabel('Average Number of Comments')
plt.xticks(rotation=45)
plt.tight_layout()
plt.savefig(os.path.join(output_directory, "images and tables/average_comments_per_thread_by_newsgroup.png"))
plt.show()
```

```{python Sentiment Score Distribution Across All Comments}
plt.figure(figsize=(10, 6))
sns.histplot(all_comments['SentimentScore'], bins=30, kde=True)
plt.title('Sentiment Score Distribution Across All Comments')
plt.xlabel('Sentiment Score')
plt.ylabel('Frequency')
plt.tight_layout()
plt.savefig(os.path.join(output_directory, "images and tables/sentiment_score_distribution_across_all_comments.png"))
plt.show()
```

@@

# Save the figure
plt.savefig(os.path.join(output_directory, "images and tables/top_25_most_active_users_by_newsgroup.png"))
plt.show()
```

@@

# Create the heatmap
plt.figure(figsize=(12, 8))
sns.heatmap(heatmap_data, cmap='viridis')
plt.title('Daily Activity Heatmap Across All Newsgroups')
plt.xlabel('Day of Week')
plt.ylabel('Hour of Day')
plt.tight_layout()
plt.savefig(os.path.join(output_directory, "images and tables/combined_daily_activity_heatmap.png"))
plt.show()
```

@@

plt.figure(figsize=(10, 6))
plt.imshow(wordcloud_all, interpolation='bilinear')
plt.axis('off')
plt.title('Most Common Words in All Usenet Comments')
plt.tight_layout()
plt.savefig(os.path.join(output_directory, "images and tables/word_cloud_all_comments.png"))
plt.show()

@@

    # Use f-string to save the file with the specific newsgroup name
    plt.savefig(os.path.join(output_directory, f"images and tables/word_cloud_{newsgroup}.png"))
    plt.show()
```

@@

# Calculate cumulative count of newsgroups created over time
plt.figure(figsize=(10, 6))
all_threads.groupby(all_threads['Date'].dt.to_period('M')).newsgroup.nunique().cumsum().plot(kind='line')
plt.title('Growth of Newsgroups Over Time')
plt.xlabel('Month')
plt.ylabel('Cumulative Number of Newsgroups')
plt.tight_layout()
plt.savefig(os.path.join(output_directory, "images and tables/growth_of_newsgroups_over_time.png"))
plt.show()
```

@@

plt.figure(figsize=(10, 6))
sns.scatterplot(data=author_stats, x='Threads_Initiated', y='Comments_Made', alpha=0.6)
plt.title('Author Engagement: Comments Made vs. Threads Initiated')
plt.xlabel('Number of Threads Initiated')
plt.ylabel('Number of Comments Made')
plt.tight_layout()
plt.savefig(os.path.join(output_directory, "images and tables/author_engagement_scatterplot.png"))
plt.show()
```

@@

plt.figure(figsize=(12, 6))
plt.plot(sentiment_over_time['Date'], sentiment_over_time['SentimentScore'], marker='o', linestyle='-')
plt.title('Average Sentiment Over Time Across All Newsgroups')
plt.xlabel('Date')
plt.ylabel('Average Sentiment Score')
plt.xticks(rotation=45)
plt.tight_layout()
plt.savefig(os.path.join(output_directory, "images and tables/sentiment_over_time.png"))
plt.show()
```

@@

plt.figure(figsize=(12, 6))
sns.boxplot(x='newsgroup', y='SentimentScore', data=all_comments)
plt.title('Sentiment Distribution by Newsgroup')
plt.xlabel('Newsgroup')
plt.ylabel('Sentiment Score')
plt.xticks(rotation=45)
plt.tight_layout()
plt.savefig(os.path.join(output_directory, "images and tables/sentiment_distribution_by_newsgroup.png"))
plt.show()
```

@@

plt.figure(figsize=(12, 8))
sns.heatmap(heatmap_data, cmap='coolwarm', center=0)
plt.title('Monthly Sentiment Heatmap by Newsgroup')
plt.xlabel('Month')
plt.ylabel('Newsgroup')
plt.xticks(rotation=45)
plt.tight_layout()
plt.savefig(os.path.join(output_directory, "images and tables/monthly_sentiment_heatmap.png"))
plt.show()
```

@@

plt.figure(figsize=(14, 8))
sns.lineplot(data=sentiment_by_newsgroup, x='Date', y='SentimentScore', hue='newsgroup', marker='o')
plt.title('Average Sentiment Over Time by Newsgroup')
plt.xlabel('Date')
plt.ylabel('Average Sentiment Score')
plt.xticks(rotation=45)
plt.tight_layout()
plt.savefig(os.path.join(output_directory, "images and tables/sentiment_over_time_by_newsgroup.png"))
plt.show()
```

@@

plt.figure(figsize=(8, 6))
sns.countplot(data=all_comments, x='SentimentPolarity', palette=['red', 'green'])
plt.title('Sentiment Polarity Distribution')
plt.xlabel('Sentiment Polarity')
plt.ylabel('Number of Comments')
plt.tight_layout()
plt.savefig(os.path.join(output_directory, "images and tables/sentiment_polarity_distribution.png"))
plt.show()
```

@@

plt.figure(figsize=(12, 6))
plt.plot(all_comments['Date'], all_comments['RollingSentiment'], color='purple')
plt.title('Sentiment Trend Analysis with Rolling Average')
plt.xlabel('Date')
plt.ylabel('Rolling Average Sentiment Score (30-day window)')
plt.xticks(rotation=45)
plt.tight_layout()
plt.savefig(os.path.join(output_directory, "images and tables/sentiment_trend_rolling_average.png"))
plt.show()
```

@@

plt.figure(figsize=(10, 6))
plt.imshow(wordcloud_positive, interpolation='bilinear')
plt.axis('off')
plt.title('Top Words in Positive Sentiment Comments')
plt.tight_layout()
plt.savefig(os.path.join(output_directory, "images and tables/word_cloud_positive_sentiment.png"))
plt.savefig(0_output_path)
plt.show()

@@

plt.figure(figsize=(10, 6))
plt.imshow(wordcloud_negative, interpolation='bilinear')
plt.axis('off')
plt.title('Top Words in Negative Sentiment Comments')
plt.tight_layout()
plt.savefig(os.path.join(output_directory, "images and tables/word_cloud_negative_sentiment.png"))
plt.show()
```

@@

# Save the network graph to an HTML file with full width and height
network_graph_path <- file.path(output_directory, "images and tables/network_graph.html")
visSave(network_graph, file = network_graph_path)

>>>>

# Initial Visualizations - Python
```{python Distribution of Comments per Newsgroup}
plt.figure(figsize=(10, 6))
sns.countplot(data=all_comments, x='newsgroup', order=all_comments['newsgroup'].value_counts().index)
plt.title('Distribution of Comments per Newsgroup')
plt.xticks(rotation=45)
plt.tight_layout()
plt.savefig(os.path.join(output_directory, "images and tables/old web visualizations/old web visualizations/distribution_of_comments_per_newsgroup.png"))
plt.show()
```

@@

plt.figure(figsize=(10, 6))
all_threads.groupby(all_threads['Date'].dt.to_period('M')).size().plot(kind='line')
plt.title('Number of Threads Across All Newsgroups Over Time')
plt.xlabel('Month')
plt.ylabel('Number of Threads')
plt.tight_layout()
plt.savefig(os.path.join(output_directory, "images and tables/old web visualizations/number_of_threads_over_time.png"))
plt.show()
```

@@

plt.figure(figsize=(10, 6))
sns.barplot(data=avg_comments_per_thread, x='newsgroup', y='Number.of.Messages', order=avg_comments_per_thread.sort_values('Number.of.Messages', ascending=False)['newsgroup'])
plt.title('Average Number of Comments per Thread by Newsgroup')
plt.xlabel('Newsgroup')
plt.ylabel('Average Number of Comments')
plt.xticks(rotation=45)
plt.tight_layout()
plt.savefig(os.path.join(output_directory, "images and tables/old web visualizations/average_comments_per_thread_by_newsgroup.png"))
plt.show()
```

```{python Sentiment Score Distribution Across All Comments}
plt.figure(figsize=(10, 6))
sns.histplot(all_comments['SentimentScore'], bins=30, kde=True)
plt.title('Sentiment Score Distribution Across All Comments')
plt.xlabel('Sentiment Score')
plt.ylabel('Frequency')
plt.tight_layout()
plt.savefig(os.path.join(output_directory, "images and tables/old web visualizations/sentiment_score_distribution_across_all_comments.png"))
plt.show()
```

@@

# Save the figure
plt.savefig(os.path.join(output_directory, "images and tables/old web visualizations/top_25_most_active_users_by_newsgroup.png"))
plt.show()
```

@@

# Create the heatmap
plt.figure(figsize=(12, 8))
sns.heatmap(heatmap_data, cmap='viridis')
plt.title('Daily Activity Heatmap Across All Newsgroups')
plt.xlabel('Day of Week')
plt.ylabel('Hour of Day')
plt.tight_layout()
plt.savefig(os.path.join(output_directory, "images and tables/old web visualizations/combined_daily_activity_heatmap.png"))
plt.show()
```

@@

plt.figure(figsize=(10, 6))
plt.imshow(wordcloud_all, interpolation='bilinear')
plt.axis('off')
plt.title('Most Common Words in All Usenet Comments')
plt.tight_layout()
plt.savefig(os.path.join(output_directory, "images and tables/old web visualizations/word_cloud_all_comments.png"))
plt.show()

@@

    # Use f-string to save the file with the specific newsgroup name
    plt.savefig(os.path.join(output_directory, f"images and tables/old web visualizations/word_cloud_{newsgroup}.png"))
    plt.show()
```

@@

# Calculate cumulative count of newsgroups created over time
plt.figure(figsize=(10, 6))
all_threads.groupby(all_threads['Date'].dt.to_period('M')).newsgroup.nunique().cumsum().plot(kind='line')
plt.title('Growth of Newsgroups Over Time')
plt.xlabel('Month')
plt.ylabel('Cumulative Number of Newsgroups')
plt.tight_layout()
plt.savefig(os.path.join(output_directory, "images and tables/old web visualizations/growth_of_newsgroups_over_time.png"))
plt.show()
```

@@

plt.figure(figsize=(10, 6))
sns.scatterplot(data=author_stats, x='Threads_Initiated', y='Comments_Made', alpha=0.6)
plt.title('Author Engagement: Comments Made vs. Threads Initiated')
plt.xlabel('Number of Threads Initiated')
plt.ylabel('Number of Comments Made')
plt.tight_layout()
plt.savefig(os.path.join(output_directory, "images and tables/old web visualizations/author_engagement_scatterplot.png"))
plt.show()
```

@@

plt.figure(figsize=(12, 6))
plt.plot(sentiment_over_time['Date'], sentiment_over_time['SentimentScore'], marker='o', linestyle='-')
plt.title('Average Sentiment Over Time Across All Newsgroups')
plt.xlabel('Date')
plt.ylabel('Average Sentiment Score')
plt.xticks(rotation=45)
plt.tight_layout()
plt.savefig(os.path.join(output_directory, "images and tables/old web visualizations/sentiment_over_time.png"))
plt.show()
```

@@

plt.figure(figsize=(12, 6))
sns.boxplot(x='newsgroup', y='SentimentScore', data=all_comments)
plt.title('Sentiment Distribution by Newsgroup')
plt.xlabel('Newsgroup')
plt.ylabel('Sentiment Score')
plt.xticks(rotation=45)
plt.tight_layout()
plt.savefig(os.path.join(output_directory, "images and tables/old web visualizations/sentiment_distribution_by_newsgroup.png"))
plt.show()
```

@@

plt.figure(figsize=(12, 8))
sns.heatmap(heatmap_data, cmap='coolwarm', center=0)
plt.title('Monthly Sentiment Heatmap by Newsgroup')
plt.xlabel('Month')
plt.ylabel('Newsgroup')
plt.xticks(rotation=45)
plt.tight_layout()
plt.savefig(os.path.join(output_directory, "images and tables/old web visualizations/monthly_sentiment_heatmap.png"))
plt.show()
```

@@

plt.figure(figsize=(14, 8))
sns.lineplot(data=sentiment_by_newsgroup, x='Date', y='SentimentScore', hue='newsgroup', marker='o')
plt.title('Average Sentiment Over Time by Newsgroup')
plt.xlabel('Date')
plt.ylabel('Average Sentiment Score')
plt.xticks(rotation=45)
plt.tight_layout()
plt.savefig(os.path.join(output_directory, "images and tables/old web visualizations/sentiment_over_time_by_newsgroup.png"))
plt.show()
```

@@

plt.figure(figsize=(8, 6))
sns.countplot(data=all_comments, x='SentimentPolarity', palette=['red', 'green'])
plt.title('Sentiment Polarity Distribution')
plt.xlabel('Sentiment Polarity')
plt.ylabel('Number of Comments')
plt.tight_layout()
plt.savefig(os.path.join(output_directory, "images and tables/old web visualizations/sentiment_polarity_distribution.png"))
plt.show()
```

@@

plt.figure(figsize=(12, 6))
plt.plot(all_comments['Date'], all_comments['RollingSentiment'], color='purple')
plt.title('Sentiment Trend Analysis with Rolling Average')
plt.xlabel('Date')
plt.ylabel('Rolling Average Sentiment Score (30-day window)')
plt.xticks(rotation=45)
plt.tight_layout()
plt.savefig(os.path.join(output_directory, "images and tables/old web visualizations/sentiment_trend_rolling_average.png"))
plt.show()
```

@@

plt.figure(figsize=(10, 6))
plt.imshow(wordcloud_positive, interpolation='bilinear')
plt.axis('off')
plt.title('Top Words in Positive Sentiment Comments')
plt.tight_layout()
plt.savefig(os.path.join(output_directory, "images and tables/old web visualizations/word_cloud_positive_sentiment.png"))
plt.savefig(0_output_path)
plt.show()

@@

plt.figure(figsize=(10, 6))
plt.imshow(wordcloud_negative, interpolation='bilinear')
plt.axis('off')
plt.title('Top Words in Negative Sentiment Comments')
plt.tight_layout()
plt.savefig(os.path.join(output_directory, "images and tables/old web visualizations/word_cloud_negative_sentiment.png"))
plt.show()
```

@@

# Save the network graph to an HTML file with full width and height
network_graph_path <- file.path(output_directory, "images and tables/old web visualizations/network_graph.html")
visSave(network_graph, file = network_graph_path)
